\documentclass{sig-alternate}


\usepackage{enumitem}
\usepackage{framed}
%\usepackage[11pt]{moresize}
\usepackage{cprotect}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{amstext}
\usepackage{amstext}
\usepackage{pdfpages}
\usepackage{alltt}
\usepackage{epstopdf}
\usepackage{xspace,colortbl}
\usepackage[USenglish]{babel}
\usepackage{multirow}
\usepackage[hyphens]{url}
\usepackage{subfigure}
\usepackage{graphicx}%%
\usepackage{amssymb}
\usepackage{fmtcount}
\usepackage{amsfonts}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[mathscr]{eucal}
%\usepackage{psfrag}
\usepackage{colortbl}

\usepackage{amsmath,amssymb}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}

\usepackage{caption}
\usepackage{graphicx}

\usepackage{bm}
\usepackage[nospace]{cite}
\usepackage{csquotes}
\usepackage{enumitem}
%\usepackage{times}

\usepackage{courier}

\lstset{basicstyle=\scriptsize\ttfamily,breaklines=true}
\lstset{framextopmargin=50pt}

\usepackage{cleveref}

\usepackage{balance}

%\linespread{0.99}

\makeatletter
\def\@copyrightspace{\relax}
\makeatother


\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand*{\QEDB}{\ensuremath{\square}}%



\begin{document}

%\setlength{\belowdisplayskip}{3pt} \setlength{\belowdisplayshortskip}{3pt}
%\setlength{\abovedisplayskip}{3pt} \setlength{\abovedisplayshortskip}{3pt}
%\setlength{\belowcaptionskip}{-10pt}
%\selectfont

\newtheorem{theorem}{Theorem}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{problem}{Problem}
\newtheorem{property}{Property}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\newcommand{\detectlib}{\texttt{IsoDetect}\xspace}
\newcommand{\company}{\texttt{Company X}\xspace}
\newcommand{\cond}{\textrm{pred}\xspace}
\newcommand{\dataset}{data set\xspace}
\newcommand{\datasets}{data sets\xspace}
\newcommand{\spview}{\textsf{SPView}\xspace}
\newcommand{\fjview}{\textsf{FJView}\xspace}
\newcommand{\aggview}{\textsf{AggView}\xspace}
\newcommand{\hashfunc}[1]{\textsf{hash}(#1)\xspace}
\newcommand{\hashop}{\textsf{hash}\xspace}
\newcommand{\nsc}{\textsf{NormalizedSC}\xspace}
\newcommand{\rsc}{\textsf{RawSC}\xspace}

\newcommand{\avgfunc}{\ensuremath{\texttt{avg} }\xspace}
\newcommand{\maxfunc}{\ensuremath{\texttt{max} }\xspace}
\newcommand{\minfunc}{\ensuremath{\texttt{min} }\xspace}
\newcommand{\histfunc}{\ensuremath{\texttt{histogram\_numeric} }\xspace}
\newcommand{\countfunc}{\ensuremath{\texttt{count}}\xspace}
\newcommand{\sumfunc}{\ensuremath{\texttt{sum} }\xspace}
\newcommand{\varfunc}{\ensuremath{\texttt{var} }\xspace}
\newcommand{\stdfunc}{\ensuremath{\texttt{std} }\xspace}
\newcommand{\covfunc}{\ensuremath{\texttt{cov} }\xspace}
\newcommand{\corrfunc}{\ensuremath{\texttt{corr} }\xspace}
\newcommand{\medfunc}{\ensuremath{\texttt{median} }\xspace}
\newcommand{\percfunc}{\ensuremath{\texttt{percentile} }\xspace}
\newcommand{\havingfunc}{\ensuremath{\texttt{HAVING} }\xspace}
\newcommand{\selectfunc}{\ensuremath{\texttt{select} }\xspace}
\newcommand{\ratio}{\ensuremath{\rho }\xspace}


\newcommand{\insertion}{\ensuremath{\texttt{INSERT} }\xspace}
\newcommand{\update}{\ensuremath{\texttt{UPDATE} }\xspace}
\newcommand{\delete}{\ensuremath{\texttt{DELETE} }\xspace}

\newcommand{\sysfull}{AlphaClean\xspace}
\newcommand{\sys}{AlphaClean\xspace}
\newcommand{\sysnospace}{AlphaClean}


\newcommand{\tbl}[1]{\textsf{#1}\xspace}
\newcommand{\field}[1]{\textsf{#1}\xspace}
\newcommand{\cost}{\textrm{cost}\xspace}
\newcommand{\ans}{\textsf{ans}\xspace}
\newcommand{\dans}{\Delta\textsf{ans}\xspace}
\newcommand{\cqp}{correction query processing\xspace}
\newcommand{\Cqp}{Correction query processing\xspace}

\newcommand{\reminder}[1]{{{\textcolor{magenta}{\{\{\bf #1\}\}}}\xspace}}
\newcommand{\ewu}[1]{{{\textcolor{blue}{\{\{\bf ewu:\} #1\}}}\xspace}}
\newcommand{\mps}[1]{{{\textcolor{red}{\{\{\bf meelap:\} #1\}}}\xspace}}
\newcommand{\stitle}[1]{\vspace{0.5em}\noindent\textbf{#1}}


\definecolor{light-gray}{gray}{0.95}
\definecolor{mid-gray}{gray}{0.85}
\definecolor{green}{RGB}{0,176,80}
\definecolor{darkred}{rgb}{0.7,0.25,0.25}
\definecolor{darkgreen}{rgb}{0.15,0.55,0.15}
\definecolor{darkblue}{rgb}{0.1,0.1,0.5}
\definecolor{orange}{RGB}{237,125,49}
\definecolor{blue}{RGB}{68,114,196}
\definecolor{pop}{RGB}{0,21,245}

\newcommand{\white}[1]{{\textcolor{white}{#1}\xspace}}
\newcommand{\blue}[1]{{\textcolor{blue}{{\bf #1}}\xspace}}
\newcommand{\orange}[1]{{\textcolor{orange}{{\bf #1}}\xspace}}
\newcommand{\pop}[1]{{\textcolor{pop}{{\textit{\textbf{#1}}}}\xspace}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\green}[1]{\textcolor{green}{#1}}
\newcommand{\gray}[1]{\textcolor{light-gray}{#1}}




\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\def\ojoin{\setbox0=\hbox{$\bowtie$}%
  \rule[-.02ex]{.25em}{.4pt}\llap{\rule[\ht0]{.25em}{.4pt}}}
\def\leftouterjoin{\mathbin{\ojoin\mkern-5.8mu\bowtie}}
\def\rightouterjoin{\mathbin{\bowtie\mkern-5.8mu\ojoin}}
\def\fullouterjoin{\mathbin{\ojoin\mkern-5.8mu\bowtie\mkern-5.8mu\ojoin}}

%\setlength{\belowcaptionskip}{-10pt}

%\newcommand{\reminder}[1] {}
\pagestyle{plain}

%\input{coverletter.tex}

\title{\sys: Iterative Learning Search for Data Cleaning}


\numberofauthors{1}
\author{ Sanjay Krishnan$\,^{*}$, Eugene Wu{$\,^{\dag\dag}$}, Michael J. Franklin$\,^{*\dag}$, Ken Goldberg$\,^{*}$,  \\
\affaddr{ $^*$UC Berkeley, ~~ $^\dag$University of Chicago, ~~ $^{\dag\dag}$Columbia University} \\
\affaddr{ \{sanjaykrishnan, franklin, goldberg\}@berkeley.edu ~~ ewu@cs.columbia.edu}\\
\affaddr{}
}

%\fontsize{9pt}{11pt}
%\selectfont


\maketitle

\begin{abstract}
Data cleaning is widely reported to be one of the most human-intensive steps in the analysis process.
We explore to what extent such transformation rules can be learned through a process of automatic trial-and-error on a dataset.
The system simulates different sequences of data transformations and scores the result according to a user-specified data quality objective function.
Inspired by recent work in AI, such as playing Go~\cite{silver2016mastering} and in Atari video games~\cite{mnih2015human}, we propose an iteratively learning search model that applies the trial-and-error procedure to small blocks of data and incrementally learns a model to prune the trials.
This basic algorithm has a number of important advantages: (1) it is highly expressive as it can model a wide range of data cleaning formalisms from integrity constraints to quantitative data cleaning in the same framework, (2) it exhibits parallelism not only over the data but also over search algorithm, and (3) the result of the algorithm is not only a cleaned database instance but transformations that can be applied to future data.
We present a system called \sys, which is built around this algorithm.
\sys additionally provides an API for specifying special-case optimizations. 
In our experiments, we find that \sys achieves parity with state-of-the-art specialized constraint, statistical, and quantitative data cleaning systems in terms of accuracy.
On two datasets considered in prior data cleaning work of Flight arrival times and a Physician registry, \sys achieves a similar precision and recall to a recently proposed (2017) Denial Constraint system called HoloClean. 
Similarly, we applied \sys to numerical outlier problems and compared to the Minimum Covariance Determinant (MCD) algorithm, which is the basis of another recent system (2017) called Macrobase.
Outliers removed by \sys  improved the accuracy of a downstream predictive models more significantly than MCD (5\% prediction accuracy improvement on the US Census Dataset) and a (4\% on an EEG dataset). 
Finally, we present initial results demonstrating the scaling properties of \sys where parallelism and caching can reduce search time by nearly two orders of magnitude.
\end{abstract}


%\pagenumbering{gobble}


\input{introduction.tex}
\input{background.tex}
\input{architecture.tex}
%\input{statement.tex}
%\input{library.tex}
\input{synth.tex}
\input{learning.tex}
\input{experiments.tex}
%\input{detector.tex}
%\input{architecture.tex}

%\input{cleaner.tex}
%\input{synthesizer.tex}
%\input{experiments.tex}
\input{relatedwork.tex}
%\input{conclusion.tex}
%\input{acks.tex}




%\bibliographystyle{abbrv}
%\scriptsize
%\fontsize{8.8pt}{9.9pt} \selectfont
\bibliographystyle{abbrv}
\bibliography{ref} 
\normalsize \selectfont

\end{document}
